Follow-up Samples

### 2017-01-09 submission/manuscript_outline_20161024.tex
update text with merge

\textbf{\emph{Bacterial Community and Fit Changes before and after
Treatment}} Based on thetayc distance metrics, comparing the initial to
the follow up samples, there was no difference between the adenoma and
carcinoma groups (P-value = 0.697) {[}Figure 1a{]}. There was a
difference in FIT between initial and follow up samples with the
carcinoma group having a significant decrease in FIT versus the adenoma
group (P-value = 2.15e-05) {[}Figure 1b{]}. Although the thetayc
distance metric change was similar between adenoma and carcinoma the
directionality of the change was significant in the cancer group between
initial and follow up (P-value = 0.002) but not for the adenoma group
(P-value = 0.997). This change can be visualized using an NMDS {[}Figure
2{]}. When all follow up samples were compared to each other there was
no significant overall difference between them (P-value = 0.085). There
was no significant difference between initial and follow up samples for
observed OTUs, Shannon diversity, or evenness after correction for
multiple comparisons {[}Table S1{]}. Time of follow up sample from
initial sampling, did not have a significant difference between adenoma
and carcinoma (uncorrected P-value = 0.784).

@@

\textbf{\emph{Statistical Analysis}} The R software package (v3.3.0) was
used for all statisitical analysis. Comparisons between bacterial
community structure utilized PERMANOVA (22) in the vegan package
(v2.4.1) while comparisons between ROC curves utilized the method by
DeLong et al. (23) executed by the pROC (v1.8) package. Comparisons
between probabilities as well as overall amount of OTU between initial
and follow up samples utilized a paired wilcoxson ranked sum test. Where
multiple comparison testing was needed a Benjamini-Hochberg (BH)
correction was applied (24) and a corrected P-value of less than 0.05
was considered significant. Unless otherwise stated the P-values
reported are those of the BH corrected ones.

@@

\textbf{Figure 1: Change in Thetayc and Fit between initial and follow
up in adenoma or carcinoma group.} A) No significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
0.697). B) A significant difference was found between the adenoma and
carcinoma group for FIT (P-value = 2.15e-05).

>>>>

\textbf{\emph{Bacterial Community and Fit Changes before and after
Treatment}} Based on thetayc distance metrics, comparing the initial to
the follow up samples, there was no difference between the adenoma and
carcinoma groups (P-value = 0.00198) {[}Figure 1a{]}. There was a
difference in FIT between initial and follow up samples with the
carcinoma group having a significant decrease in FIT versus the adenoma
group (P-value = 2.15e-05) {[}Figure 1b{]}. Although the thetayc
distance metric change was similar between adenoma and carcinoma the
directionality of the change was significant in the cancer group between
initial and follow up (P-value = 0.002) but not for the adenoma group
(P-value = 0.997). This change can be visualized using an NMDS {[}Figure
1c \& 1d{]}. When all follow up samples were compared to each other
there was no significant overall difference between them (P-value =
0.085). There was no significant difference between initial and follow
up samples for observed OTUs, Shannon diversity, or evenness after
correction for multiple comparisons {[}Table S1{]}. Time of follow up
sample from initial sampling, did not have a significant difference
between adenoma and carcinoma (uncorrected P-value = 0.784).

@@

\textbf{\emph{Statistical Analysis}} The R software package (v3.3.2) was
used for all statisitical analysis. Comparisons between bacterial
community structure utilized PERMANOVA (22) in the vegan package
(v2.4.1) while comparisons between ROC curves utilized the method by
DeLong et al. (23) executed by the pROC (v1.8) package. Comparisons
between probabilities as well as overall amount of OTU between initial
and follow up samples utilized a paired wilcoxson ranked sum test. Where
multiple comparison testing was needed a Benjamini-Hochberg (BH)
correction was applied (24) and a corrected P-value of less than 0.05
was considered significant. Unless otherwise stated the P-values
reported are those of the BH corrected ones.

@@

\textbf{Figure 1: Change in Thetayc and Fit between initial and follow
up in adenoma or carcinoma group.} A) No significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
0.00198). B) A significant difference was found between the adenoma and
carcinoma group for FIT (P-value = 2.15e-05).
